\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Editing Section 2

@@

\medskip
Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes. A comprehensive review of mechanisms of fluid instabilities (i.e., fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces and is often referred as viscous instabilities or viscous fingering.

\medskip
In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}). Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells. Viscous instabilities are mainly governed by the mobility ratio (MR) between the displacing and the displaced fluids. Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.

@@

\medskip
The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries. %FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions. %Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times. %At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains. FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions. The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions. Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times. 
Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements. In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}. Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.

@@

Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}. This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.

All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs. In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$. For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$. Fluids are assumed incompressible and gravity was neglected. The set-up for the numerical simulations are summarised in Table \ref{table:setup}.

@@

\medskip
The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

@@

\medskip
A number of different cases have been illustrated in Section \ref{section:results}. Starting from tested experimental cases and geometrical domains to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied. Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces on the developement of the flows. For immiscible displacements upon which only viscous and capillary forces are acting (being horizontal flow, gravity can be ignored), the expected displacement patterns are either stable front displacement or unstable front displacement. In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number ($N_{c}$) but mainly on mobility ratio (MR). If the mobility ratio is significantly less than $5$ (MR=$3$ has been used) , it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate. On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate. Therefore for an i.e., water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil. Hence, the displacement form could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.

@@

\medskip
Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.

\medskip
In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}). Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells. Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids. Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.

@@

\medskip
Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements. In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}. Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.

@@

Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}. This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.

All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs. In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$. For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$. Fluids are assumed incompressible and gravity was neglected. The set-up for the numerical simulations are summarised in Table \ref{table:setup}.

@@

\medskip
The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

>>>>

\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
\newcommand{\KCnote}[1]{\fbox{\parbox{\textwidth}{ \color{black} KC Note $\Rightarrow$ #1}}}
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\green}{\textcolor{green}}
\journal{Advances in Water Resources}
\newcommand{\frc}{\displaystyle\frac}
\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
\newcommand{\eg}{{\it e.g.,}} 
\newcommand{\ie}{{\it i.e.,}}

@@

\medskip
Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes. A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces and is often referred as viscous instabilities or viscous fingering.

\medskip
In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}). Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells. Viscous instabilities are mainly governed by the mobility ratio (MR) between the displacing and the displaced fluids. Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.

@@

\medskip
The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries. %FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions. %Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times. %At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains. FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions. The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions. Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times. 
Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements. In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}. Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.

@@

Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}. This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.

All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs. In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$. For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$. Fluids are assumed incompressible and gravity was neglected. The set-up for the numerical simulations are summarised in Table \ref{table:setup}.

@@

\medskip
The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media. The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

@@

\medskip
A number of different cases have been illustrated in Section \ref{section:results}. Starting from tested experimental cases and geometrical domains to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied. Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces on the developement of the flows. For immiscible displacements upon which only viscous and capillary forces are acting (being horizontal flow, gravity can be ignored), the expected displacement patterns are either stable front displacement or unstable front displacement. In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number ($N_{c}$) but mainly on mobility ratio (MR). If the mobility ratio is significantly less than $5$ (MR=$3$ has been used) , it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate. On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate. Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil. Hence, the displacement form could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.

@@

\medskip
Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (\ie fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.

\medskip
In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}). Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells. Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids. Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.

@@

\medskip
Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements. In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}. Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.

@@

Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}. This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.

All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs. In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$. For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$. Fluids are assumed incompressible and gravity was neglected. The set-up for the numerical simulations are summarised in Table \ref{table:setup}.

@@

\medskip
The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

### 2017-06-19 Papers/ViscousInstabilities/article_figure1.tex
Editing Section 2

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
\caption{This is a description of two different element types. Element A is the \PN[1]{2}, while element B is the \PN[1]{1} \red{(THIS IS NOT CORRECT!!)}. Porosity $\phi_{i}$ \red{(THIS DOES NOT APPEAR IN THE FIGURE ... AT LEAST NOT WITH THIS SYMBOL)} and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space. Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
\label{fig:fem_elem}
\end{figure}

@@

\begin{comment}
%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.0cm} (a)  
}
\vspace{0.5cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
}
\vspace{1.0cm}
\hbox{\hspace{6.0cm} (b)  
}}     
\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
\label{fem_cv_represent_a}
\end{figure}
\clearpage
\end{comment}

@@

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
\caption{This is a description of two different element types. Element A is the \PN[1]{2}, while element B is the \PN[1]{1} \red{(THIS IS NOT CORRECT!!)}. Porosity $\phi_{i}$ \red{(THIS SYMBOL DOES NOT APPEAR IN THE FIGURE !!)} and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space. Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
\label{fig:fem_elem}
\end{figure}

@@

@@

%%%
%%% FIGURE
%%%
\begin{landscape}
  \begin{figure}[ht]
    \vbox{ 
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
      \hbox{\hspace{10cm} (a) VR = 1}
      \vspace{1cm}
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf} }
      \hbox{\hspace{10cm} (b) VR = 10  }}
\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10 (the domain contains \red{XX} elements).}
\label{fem_cv_represent_a}
\end{figure}
\end{landscape}
\clearpage
%%%
%%%
%%%

### 2017-06-19 Papers/ViscousInstabilities/article_table.tex
Editing Section 2

\begin{landscape}
\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
    \hline
      \ref{section:results_validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
      \ref{section:results_homo_hete}  & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
      \ref{section:results_hete_fix_adapt}  & 0.2  & 1.0  & 0.0  & 1.0  &  3.0  & 2.0  & 5.0  & 1.0  & N/A & 0.2  & 0.3 & XX  \\
      \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $0$ denotes initial condition. \red{(KOSTAS, PLEASE: 1. DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2. REPLACE ALL XX; 3. COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS.  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}\label{table:setup}
\end{table}
\end{landscape}
\clearpage

>>>>

\begin{landscape}
\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
    \hline
     \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 1.0 & 2.5 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.0 & N/A & N/A & N/A & 0.2 & 0.3 & XX  \\
     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 -- & 1.e-12 -- & 1.e-12 -- & 1.e-10 & 0.2  & 0.3 & 1.0 \\
      &   &  &  &  & 5.e-10 & 5.e-10 & 1.e-10  &  &  &  & \\
     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & XX  \\
     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & XX  \\
     \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $0$ denotes initial condition. \blue{(PLEASE: 1. DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2. \underline{REPLACE ALL \red{XX}}; 3. COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS.  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}\label{table:setup}
\end{table}
\end{landscape}
\clearpage
